Timely Object Recognition

### 2012-06-01 writeups/nips12/evaluation.tex
printed

We evaluate our system on the multi-class, multi-label detection task as previously described.
Each detection episode takes an image and outputs detections with associated times, based on the order of actions taken.
We evaluate on a popular detection challenge task: the PASCAL VOC 2007 dataset \cite{pascal-voc-2010}.
As shown in \autoref{fig:dataset_stats}, the dataset exhibits a rather modest amount of class co-occurrence.

@@

We test three different settings of the start and deadline times.
In the first one, the start time is immediate and execution is cut off at 20 seconds, which is enough time to run basically all actions.
In the second one, execution is cut off after only 10 seconds.
Lastly, we measure performance between 5 seconds and 15 seconds.
These operating points show how our method would behave when deployed in different conditions.

\begin{figure}[h!]
\centering
\subfloat[AP vs. Time curves for Random, Oracle, the Fixed Order baseline, and our best-performing policy, with start time of 5 seconds and deadline of 15 seconds.]{
\includegraphics[width=0.47\linewidth]
    {../figures/final1_515.png}\label{fig:results1}} \hfill
\subfloat[Reward function explanation]{
\includegraphics[width=0.47\linewidth]
    {../figures/apvst_expl.pdf}\label{fig:rewards}}
\end{figure}

@@

In Figure \autoref{fig:results1}, we can see that due to the dataset bias, the fixed-order policy performs well at first (as can be seen in \autoref{fig:dataset_stats}, the person class is disproportionately likely to be in the image), but is significantly overtaken by our model as execution goes on.

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.86\linewidth]{../figures/trajectories.pdf}
  \caption{\todo{trajectories}}
  \label{fig:trajectories}
\end{figure}

@@

\begin{table}[t]
\caption{Results}
\label{tab:results}
\begin{center}
\begin{tabular}{|l|l|l|l|l|l|}
%\\ \hline \\
\hline
Bounds & Random & Fixed Order & RL w/ MRF & w/ GIST  & Oracle \\ \hline
(0,10) & 0.119  & 0.240       & 0.266     & \textbf{0.267}    & 0.464 \\ 
(0,20) & 0.250  & 0.342       & 0.378     & 0.382    & 0.488 \\ 
(5,15) & 0.257  & 0.362       & 0.418     & 0.420    & 0.530 \\ \hline
\end{tabular}
\end{center}
\end{table}

\todo{something about setting values?}

>>>>

We evaluate our system on the multi-class, multi-label detection task as previously described.
Each detection episode takes an image and outputs detections with associated times, based on the order of actions taken.
We evaluate on a popular detection challenge task: the PASCAL VOC 2007 dataset \cite{pascal-voc-2010}, which exhibits only a rather modest amount of class co-occurrence: the ``person'' class is highly likely to occur, and less than $10\%$ of the images have more than two classes.

@@

We test three different settings of the start and deadline times.
In the first one, the start time is immediate and execution is cut off at $20$ seconds, which is enough time to run basically all actions.
In the second one, execution is cut off after only $10$ seconds.
Lastly, we measure performance between $5$ seconds and $15$ seconds.
These operating points show how our method behaves when deployed in different conditions.
The results are given in rows of \autoref{tab:results}.

\begin{figure}[h!]
\centering
\subfloat[AP vs. Time curves for Random, Oracle, the Fixed Order baseline, and our best-performing policy, with start time of 5 seconds and deadline of 15 seconds.]{
\includegraphics[width=0.47\linewidth]
    {../figures/final1_515.png}\label{fig:results1}} \hfill
\subfloat[Reward function explanation]{
\includegraphics[width=0.47\linewidth]
    {../figures/apvst_expl.pdf}\label{fig:rewards}}
\caption{}
\end{figure}

@@

In Figure~\autoref{fig:results1}, we can see that due to the dataset bias, the fixed-order policy performs well at first, as the person class is disproportionately likely to be in the image, but is significantly overtaken by our model as execution goes on and more rare classes have to be detected.

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.86\linewidth]{../figures/trajectories.pdf}
  \caption{
Visualizing the action trajectories of different policies.
The orange lines show the action selections over many episodes; the size of the blue circles correspond to the $\Delta ap$ obtained by the action.
We see that the \textbf{Random} policy selects actions and obtains rewards randomly, while the \textbf{Oracle} policy obtains all rewards in the first few actions.
The \textbf{Fixed Order} policy selects actions in a static optimal order.
Our policy does not stick a static order but selects actions dynamically to maximize the rewards obtained early on.
}
  \label{fig:trajectories}
\end{figure}

@@

\begin{table}[t]
\caption{Results}
\label{tab:results}
\begin{center}
\begin{tabular}{|l|l|l|l|l|l|}
\hline
Bounds & Random & Fixed Order & RL w/ MRF & w/ GIST         & Oracle \\ \hline
(0,20) & 0.250  & 0.342       & 0.378     & \textbf{0.382}  & 0.488 \\ 
(0,10) & 0.119  & 0.240       & 0.266     & \textbf{0.267}  & 0.464 \\ 
(5,15) & 0.257  & 0.362       & 0.418     & \textbf{0.420}  & 0.530 \\ \hline
\end{tabular}
\end{center}
\end{table}

%\todo{something about setting values?}

### 2012-06-01 writeups/nips12/technical.tex
printed

Although the action space $\mathcal{A}$ is quite manageable, consisting of the detectors and classifier we would like to run on the image, the space of possible states $S$ is infinite.
Therefore we cannot learn a tabular representation of $Q(s,a)$, and must use function approximation to represent it \cite{Sutton1998}.
We featurize the state-action pair and assume linear structure:
\begin{align}
Q^\pi(s,a_i) = \theta_\pi^\top  \phi(s,a_i)
\end{align}

@@

We can then represent the final evaluation in terms of individual rewards:
\begin{align}
eval(h) = \sum_{j=0}^J R(s^j,a^j)
\end{align}

@@

Additionally, we include the mean and maximum entropies of all classes, time features that represent the times until start and deadline, and the expected time (cost) of the action, for a total of $F$ features.

@@

\begin{figure}[h!]
\centering
\subfloat[Greedy]{\includegraphics[width=0.49\linewidth]{../figures/weights_greedy}}
\subfloat[RL]{\includegraphics[width=0.49\linewidth]{../figures/weights_rl}}
% \includegraphics[width=0.87\linewidth]{../figures/weights.pdf}
\caption{Weights \todo{describe. can talk about the person-class weights, the role of the time weights. how you can see the co-occurrence matrix in the weights}}
\label{fig:weights}
\end{figure}

@@

The graphical model structure is set as fully-connected, but as shown in \autoref{fig:dataset_stats}, some classes are overwhelmingly unlikely to co-occurr.
Accordingly, the graph edge weights are learned with $L_1$ regularization, which obtains the desired sparse structure \cite{Lee2006}.
All parameters of the model are trained on fully-observed data, and inference is implemented with an open-source graphical model package \cite{Jaimovich2010}.
As exact inference is generally intractable in this model, we use Loopy Belief Propagation; although it does not provide general convergence guarantees, it has been shown to work well empirically on similar tasks \cite{Desai2009}.

>>>>

Although the action space $\mathcal{A}$ is quite manageable, consisting of the detectors and classifier we would like to run on the image, the space of possible states $S$ is infinite.
Therefore we cannot learn a tabular representation of $Q(s,a)$, and must use function approximation to represent it \cite{Sutton1998}.
We featurize the state-action pair and assume linear structure: $Q^\pi(s,a_i) = \theta_\pi^\top  \phi(s,a_i)$.

@@

We can then represent the final evaluation $eval(h,T_s,T_d)$ in terms of individual rewards: $\sum_{j=0}^J R(s^j,a^j)$.

@@

Additionally, we include the mean and maximum entropies of all classes, the expected time (cost) of the action, and time features that represent the times until start and deadline, for a total of $F$ features.

@@

\begin{figure}[h!]
\centering
\subfloat[Greedy]{\includegraphics[width=0.49\linewidth]{../figures/weights_greedy}}
\subfloat[RL]{\includegraphics[width=0.49\linewidth]{../figures/weights_rl}}
% \includegraphics[width=0.87\linewidth]{../figures/weights.pdf}
\caption{
Learned policy weights $\theta_\pi$ (best viewed in color: red corresponds to positive, blue to negative values).
The first row corresponds to the scene-level action, which does not generate detections itself but only helps reduce uncertainty about the contents of the image.
Note that in the greedy learning case, this action is learned to never be taken---whereas it is shown to be useful in the reinforcement learning case.
}
\label{fig:weights}
\end{figure}

@@

The graphical model structure is set as fully-connected, but some classes are overwhelmingly unlikely to co-occurr in our dataset.
Accordingly, the graph edge weights are learned with $L_1$ regularization, which obtains the desired sparse structure \cite{Lee2006}.
All parameters of the model are trained on fully-observed data, and Loopy Belief Propagation inference is implemented with an open-source graphical model package \cite{Jaimovich2010}.
% As exact inference is generally intractable in this model, we use Loopy Belief Propagation; although it does not provide general convergence guarantees, it has been shown to work well empirically on similar tasks \cite{Desai2009}.
